### 2019-03-15 paper_5.tex
modify abstract

本原型系统立足目前司法领域的核心需求，种族要设计了案情要素提取，类案语义匹配，类案检索以及法条推荐四部分核心功能，为法官判案进行司法辅助，实现司法判决的一致性，提高法官办案效率，为民众提供法律咨询，提供司法领域智能化水平，实现司法公正。本原型系统的整体功能设计如图\ref{fig:sys_main}：
\begin{figure*}[htbp]%[htbp]
    \centering
    \includegraphics[scale=0.5, clip=true]{./sources/sys_main.eps}
    \caption{\label{fig:sys_main}系统功能总体设计图}
\end{figure*}

>>>>

本原型系统立足目前司法领域的核心需求，主要设计了案情要素提取，类案语义匹配，类案检索以及法条推荐四部分核心功能，为法官判案进行司法辅助，实现司法判决的一致性，提高法官办案效率，为民众提供法律咨询，提供司法领域智能化水平，实现司法公正。本原型系统的整体功能设计如图\ref{fig:sys_main}：
\begin{figure*}[htbp]%[htbp]
    \centering
    \includegraphics[scale=0.5, clip=true]{./sources/sys_main.eps}
    \caption{\label{fig:sys_main}系统功能总体设计图}
\end{figure*}

### 2019-03-15 paper_abstract.tex
modify abstract

\end{cabstract}

@@

>>>>

最后，本课题设计并实现了一个原型系统。该原型系统立足法官的基本需求，基于本课题提出的上述两个模型，设计实现了裁判文书要素提取，裁判文书语义匹配，类案检索，判决预测四个功能，在实际场景下对模型的应用进行了实验，有效证明了本课题模型的实际应用价值。
\end{cabstract}

@@

Finally, a prototype system is designed and implemented. The prototype system is based on the basic needs of judges. Based on the above two models proposed in this topic, four functions are designed and implemented, namely, extracting elements of judgment documents, semantic matching of judgment documents, case retrieval and judgment prediction. The application of the model in actual scenarios is experimented, which effectively proves the practical application value of the model.
